---
title: "Kallisto"
author: "Roberto Alvarez"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## Descargar datos FASTQ



```{r eval=FALSE}
#!/bin/bash
mkdir data
cd data
for i in `seq 25 40`; 
do 
  mkdir DRR0161${i}; 
  cd DRR0161${i}; 
  wget ftp://ftp.sra.ebi.ac.uk/vol1/fastq/DRR016/DRR0161${i}/DRR0161${i}_1.fastq.gz; 
  wget ftp://ftp.sra.ebi.ac.uk/vol1/fastq/DRR016/DRR0161${i}/DRR0161${i}_2.fastq.gz; 
  cd ..; 
done
cd .. 
```




## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.
